### 2021-05-23 docs/manuscript/manuscript.tex
Include Munteanu et al. 2014 in introduction

Cotterell and Sharpe studied what kind of 3-node network topologies could
interact with a morphogen gradient and produce a stripe of gene expression
in a one-dimensional field of cells and found a variety of networks that
implemented at least 7 different mechanisms and had different levels of
complexity \cite{Cotterell2010}.

>>>>

Producing a stripe of gene expression is a fundamental patterning function
in development, and it has been shown that feed-forward motifs are minimal
networks capable of performing this function \cite{munteanu_2014}. For example,
Cotterell and Sharpe studied what kind of 3-node network topologies could
interact with a morphogen gradient and produce a stripe of gene expression
in a one-dimensional field of cells and found a variety of networks that
implemented at least 7 different mechanisms and had different levels of
complexity, being most of them variations of feed-forward motifs \cite{Cotterell2010}.
